\documentclass[a4paper,10pt]{article}
\pagestyle{empty}
\usepackage{hyperref}
\usepackage{palatino}
\usepackage[american,USenglish]{babel}
\usepackage{graphicx}
\usepackage[leqno]{amsmath}
\usepackage[margin=1.5cm,vmargin={0pt,1cm},includefoot]{geometry}
\title{}
\author{Mark Johnson \\
Loyola University Chicago}
\date {mjohnson4@luc.edu}
% End of preamble,
% the body now follows
\begin{document}
\maketitle

\section{Problem 1C}
\emph{Consider a pool of six I/O buffers. Assume that any buffer is just as likely to be available (or occupied) as 
any other. Compute the probability associated with the following event: \newline
C = "All buffers available or an even number of buffers occupied."} [Trivendi, 1982]
\subsection{Step 1: (Identify the sample space S)}
The points in the chosen sample space must be mutually exclusive and collectively exhaustive. The former means that 
no two points in the sample space can occur simultaneously. The latter means that the outcome from any trial must be 
exactly one point from the sample space. We are counting the number of ways we can select k objects from among n 
objects where order is important and the same object can be repeated any number of times. Because the sample space 
can be defined as ordered samples of size k with replacements (permutations with replacements), and because each 
sample point represents one of these permutations, we assert that the sample space has $ n^{k} $ or $ 2^{6} $ sample 
points. We assert that the sample space defined below is mutually exclusive and collectively exhaustive. \newline
$ S = \{ s_{0}, s_{1}, s_{2}, s_{3},...s_{63} \} $ where \newline
$ s_{0} = \{0,0,0,0,0,0\}, s_{1} = \{0,0,0,0,0,1\}, s_{2} = \{0,0,0,0,1,0\}, s_{3} = \{0,0,0,0,1,1\},...,s_{63} = 
\{1,1,1,1,1,1\} $

\subsection{Step 2: (Assign probabilities)}
Because the problem statement specifies that each event is equiprobable, each sample point has a probability of $ 
\frac{1}{S} $ or $ \frac{1}{64} $.

\subsection{Step 3: (Identify the events of interest)}
C = "All buffers available or an even number of buffers occupied." \newline
C = Zero, Two, Four, or Six buffers occupied. \newline
$ C = \{c_{0}, c_{1}, c_{2}, c_{3}\} $ where: \newline
$ c_{0} = $ Zero buffers occupied. \newline
$ c_{1} = $ Two buffer occupied. \newline
$ c_{2} = $ Four buffers occupied. \newline
$ c_{3} = $ Six buffers occupied. \newline
$ c_{0} = \{(0,0,0,0,0,0)\} $ \newline
Therefore, $ c_{0} = \{s_{0}\} $. \newline
$ c_{1} = \{(0,0,0,0,1,1), (0,0,0,1,0,1), (0,0,0,1,1,0), (0,0,1,0,0,1), (0,0,1,0,1,0), (0,0,1,1,0,0), $ \newline
$ (0,1,0,0,0,1), (0,1,0,0,1,0), (0,1,0,1,0,0), (0,1,1,0,0,0), (1,0,0,0,0,1), (1,0,0,0,1,0), (1,0,0,1,0,0), $ \newline
$ (1,0,1,0,0,0), (1,1,0,0,0,0)\} $ \newline
Therefore, $ c_{1} = \{s_{3}, s_{5}, s_{6}, s_{9}, s_{10}, s_{12}, s_{17}, s_{18}, s_{20}, s_{24}, $ \newline
$ s_{33}, s_{34}, s_{36}, s_{40}, s_{48}\} $ \newline
$ c_{2} = \{(0,0,1,1,1,1), (0,1,0,1,1,1), (0,1,1,0,1,1), (0,1,1,1,0,1), (0,1,1,1,1,0), (1,0,0,1,1,1),$ \newline
$ (1,0,1,0,1,1), (1,0,1,1,1,0), (1,1,0,0,1,1), (1,1,0,1,0,1), (1,1,0,1,1,0), (1,1,1,0,0,1), (1,1,1,0,1,0), $ \newline
$ (1,1,1,1,0,0)\} $ \newline
Therefore, $ c_{2} = \{s_{15}, s_{23}, s_{27}, s_{29}, s_{30}, s_{39}, s_{43}, s_{46}, s_{51}, s_{53}, $ \newline
$ s_{54}, s_{57}, s_{58}, s_{60} $ \newline
$ c_{3} = \{1,1,1,1,1,1\} $ \newline
$ c_{3} = \{s_{63}\} $ \newline
\subsection{Step 4: (Compute desired probabilities)}
$ C = \{c_{0}, c_{1}, c_{2}, c_{3}\} $ \newline
$ C = c_{0} \cup c_{1} \cup c_{2}, \cup c_{3} $ \newline
$ P(C) = P(c_{0}) + P(c_{1}) + P(c_{2}) + P(c_{3}) $ \newline
$ P(c_{0}) = \frac{1}{64} $ \newline
$ P(c_{1}) = \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + 
\frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} $ \newline  
$ + \frac{1}{64} + \frac{1}{64} $ \newline
$ P(c_{1}) = \frac{15}{64} $ \newline
$ P(c_{2}) = \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} +
\frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} + \frac{1}{64} $ \newline
$ + \frac{1}{64} + \frac{1}{64} $ \newline 
$ P(c_{2}) = \frac{15}{64} $ \newline
$ P(c_{3}) = \frac{1}{64} $ \newline
$ P(C) = \frac{1}{64} + \frac{15}{64} + \frac{15}{64} + \frac{1}{64} $ \newline
$ P(C) = \frac{32}{64} $ \newline
$ P(C) = \frac{1}{2} $ \newline
Therefore, the probability that all buffers are available or an even number of buffers are occupied is 0.50. \newline
\end{document} X
